Analysis of Major Crimes in Toronto And Suggestions on How to Protect Ourselves

### 2024-01-23 outputs/paper/paper.qmd
finish conclusion

---
title: "Analysis of Major Crimes in Toronto And Suggestions on How to Protect Ourselves"
author: "Boxuan Yi"
date: 20 January 2024
abstract: "Safety is one of the most important factors that people consider when deciding where to live and go. This report uses data from Open Data Toronto to analyze the occurrences of various types of crimes in different regions and time of Toronto, as well as the trend over the past ten years. The result shows that Downtown Toronto and evenings & noon have a relatively high occurrences of crimes, which could be used as a suggestion on both individual and government dicision-making."
format: pdf
bibliography: references.bib
---
## Introduction
On Dec 25th, 2023, the Christmas Day, a news has raised huge concerns among people — a man was seriously injured after stabbing in downtown Toronto. This was not the first such incident on that block in December; unfortunately, such distressing news has become more and more prevalent nowadays. As the pandemic comes to an end, there is a noticeable increase in people returning to the office and going out more frequently than in previous years. Naturally, public safety and private security have become particularly crucial, leading to a significant question: How can we proactively prevent such incidents from affecting ourselves and our loved ones?

@@

## Data

### Data Source and Software
The data utilized throughout this paper, in csv format, was obtained from Toronto Police Services on the City of Toronto Open Data Website [@rOpenDataToronto], with the title “MAJOR CRIME INDICATORS”.

@@

### Data Collection
The dataset contains all Major Crime Indicators occurrences by report data. The categories of major crimes are Assault, Break and Enter, Auto Theft, Robbery and Theft Over. The latest refresh was on Jan 11, 2024.

@@

### Data Analysis and Visualizations
The Major Crimes in Toronto dataset contains 27 columns and 372899 rows, including the repeated occurrences with different crime categories. All the samples of major crimes were reported from 2014 to 2023. Among 27 columns, the variables I will use are x_id, report_year, occ_year, occ_month, occ_dow (Day of the Week Offence Occurred), occ_hour, mci_category, division. I will create two more variables, division_area, which classifies 18 police divisions (including a NSA) into 6 regions of Toronto (including Other for NSA), and weekend_weekday, which indicates whether the occurrence happen on a weekday or a weekend.

@@

```{r}
#| include: false
clean_mci_data <- clean_mci_data |> 
  mutate(
    weekday_weekend =
      case_match(
        occ_dow,
        "Wednesday" ~ "Weekday",
        "Tuesday" ~ "Weekday",
        "Thursday" ~ "Weekday",
        "Sunday" ~ "Weekend",
        "Monday" ~ "Weekday",
        "Friday" ~ "Weekday",
        "Saturday" ~ "Weekend",
        "" ~ "Other"))
clean_mci_data
```
There are 18 police divisions, which are D11, D12, D13, D14, D22, D23, D31, D32, D33, D41, D42, D43, D51, D52, D53, D54, D55, and NSA. I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other. 
```{r}
#| message: false
#| echo: false
#| label: tbl-division_area
#| tbl-cap: Police divisions in 6 areas(including other)

clean_mci_data%>%
  group_by(division_area) %>%
  summarise(division = toString(unique(division))) |> kable()

@@

Based on Figure 2, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest. North York, Scarborough, and Etobicoke-York have similar numbers, but the rate of increase in North York is higher than that observed in the other two.

@@

```{r}
# Share
```

## Conclusion
In summary, ‘Assault’ has always ranked as the most common major crime over the past ten years. However, the difference between ‘Auto Theft’ and ‘Assault’ is shrinking, as the number of ‘Auto Theft’ is increasing rapidly. There need be more safety actions on automobiles, and people should lock the doors and not leave any packages visible through car windows to improve automobile security. Due to the difficulty to prove ‘Assault’ as a crime, installing cameras at the front door or home security systems is a good idea to provide evidence for ‘Assault’, while it can also record suspicious individuals and vehicles near one's residence. Taking proactive steps, such as responding to knocks cautiously while keeping the door locked, and refraining from touching anything until the police have inspected, is crucial for personal safety and should be instilled in children as well.

@@

\newpage

## References

>>>>

---
title: "Analysis of Major Crimes in Toronto And Suggestions on How to Protect Ourselves"
author: "Boxuan Yi"
date: 20 January 2024
thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/Sta302_Major_Crime_Indicators"
abstract: "Safety is one of the most important factors that people consider when deciding where to live and go. This report uses data from Open Data Toronto to analyze the occurrences of various types of crimes in different regions and time of Toronto, as well as the trend over the past ten years. The result shows that Downtown Toronto and evenings & noon have a relatively high occurrences of crimes, which could be used as a suggestion on both individual and government dicision-making."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
# Introduction
On Dec 25th, 2023, the Christmas Day, a news has raised huge concerns among people — a man was seriously injured after stabbing in downtown Toronto. This was not the first such incident on that block in December; unfortunately, such distressing news has become more and more prevalent nowadays. As the pandemic comes to an end, there is a noticeable increase in people returning to the office and going out more frequently than in previous years. Naturally, public safety and private security have become particularly crucial, leading to a significant question: How can we proactively prevent such incidents from affecting ourselves and our loved ones?

@@

# Data

## Data Source and Software
The data utilized throughout this paper, in csv format, was obtained from Toronto Police Services on the City of Toronto Open Data Website [@rOpenDataToronto], with the title “MAJOR CRIME INDICATORS”.

@@

## Data Collection
The dataset contains all Major Crime Indicators occurrences by report data. The categories of major crimes are Assault, Break and Enter, Auto Theft, Robbery and Theft Over. The latest refresh was on Jan 11, 2024.

@@

## Data Analysis and Visualizations
The Major Crimes in Toronto dataset contains 27 columns and 372899 rows, including the repeated occurrences with different crime categories. All the samples of major crimes were reported from 2014 to 2023. Among 27 columns, the variables I will use are x_id, report_year, occ_year, occ_month, occ_dow (Day of the Week Offence Occurred), occ_hour, mci_category, division. I will create two more variables, division_area, which classifies 18 police divisions (including a NSA) into 6 regions of Toronto (including Other for NSA), and weekend_weekday, which indicates whether the occurrence happen on a weekday or a weekend.

@@

```{r}
#| include: false
clean_mci_data <- clean_mci_data |> 
  mutate(
    weekday_weekend =
      case_match(
        occ_dow,
        "Wednesday" ~ "Weekday",
        "Tuesday" ~ "Weekday",
        "Thursday" ~ "Weekday",
        "Sunday" ~ "Weekend",
        "Monday" ~ "Weekday",
        "Friday" ~ "Weekday",
        "Saturday" ~ "Weekend",
        "" ~ "Other"))
clean_mci_data
```
There are 18 police divisions, which are D11, D12, D13, D14, D22, D23, D31, D32, D33, D41, D42, D43, D51, D52, D53, D54, D55, and NSA. I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other, as shown in Table 2.Based on Figure 2, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest. North York, Scarborough, and Etobicoke-York have similar numbers, but the rate of increase in North York is higher than that observed in the other two. 
```{r}
#| message: false
#| echo: false
#| label: tbl-division_area
#| tbl-cap: Police divisions in 6 areas(including other)

clean_mci_data |>
  group_by(division_area) |>
  summarise(division = toString(unique(division))) |> kable()

@@

@@

```{r}
#| include: false
# Share
```

\newpage
# Conclusion
In summary, ‘Assault’ has always ranked as the most common major crime over the past ten years. However, the difference between ‘Auto Theft’ and ‘Assault’ is shrinking, as the number of ‘Auto Theft’ is increasing rapidly. There need be more safety actions on automobiles, and people should lock the doors and not leave any packages visible through car windows to improve automobile security. Due to the difficulty to prove ‘Assault’ as a crime, installing cameras at the front door or home security systems is a good idea to provide evidence for ‘Assault’, while it can also record suspicious individuals and vehicles near one's residence. Taking proactive steps, such as responding to knocks cautiously while keeping the door locked, and refraining from touching anything until the police have inspected, is crucial for personal safety and should be instilled in children as well.

@@

\newpage
# References
